%\chapter{Bibliography}

\medskip

~~~[1] Learning Realistic Human Reposing using Cyclic Self-Supervision with 3D Shape, Pose, and Appearance Consistency (2021)\\Soubhik Sanyal, Alex Vorobiov, Timo Bolkart, Matthew Loper, Betty Mohler, Larry Davis, Javier Romero, Michael J. Black
\url{https://arxiv.org/abs/2110.05458v1}

\medskip

[2] End-to-end Recovery of Human Shape and Pose (2018)\\Angjoo Kanazawa, Michael J. Black, David W. Jacobs, Jitendra
\url{https://arxiv.org/abs/1712.06584}

\medskip

[3] Human3.6m\\Catalin Ionescu, Dragos Papava, Vlad Olaru, Cristian Sminchisescu
\url{http://vision.imar.ro/human3.6m/description.php}

\medskip

[4] Moulding Humans: Non-parametric 3D Human Shape Estimation from Single Images (2019)\\
Valentin Gabeur, Jean-Sébastien Franco, Xavier Martin, Cordelia Schmidt, Grégory Rogez
\url{https://openaccess.thecvf.com/content_ICCV_2019/papers/Gabeur_Moulding_Humans_Non-Parametric_3D_Human_Shape_Estimation_From_Single_Images_ICCV_2019_paper.pdf}

\medskip

[5] BodyNet: Volumetric Inference of 3D Human Body Shapes (2018)\\
Gül Varol, Duygu Ceylan, Bryan Russell, Jimei Yang, Ersin Yumer, Ivan Laptev, Cordelia Schmid
\url{https://arxiv.org/abs/1804.04875}

\medskip

[6] SMPL: A Skinned Multi-Person Linear Model (2015)\\
Matthew Loper, Naureen Mahmood, Javier Romero, Gerard Pons-Moll, Michael J. Black.

\medskip

[7] High-level clothes description based on colour-texture and structural features (2003)
In Pattern Recognition and Image Analysis, pages 108–116.\\
A. Borràs, F. Tous, J. Lladós, and M. Vanrell.

\medskip

[8] A 2D human body model dressed in eigen clothing (2010)
ECCV, pages 285-298.\\
P. Guan, O. Freifeld, and M. J. Black.

\medskip

[9] Estimating body shape of dressed humans (2009)
Computer and graphics, pages 211-219.\\
N. Hasler, C. Stoll, B. Rosenhahn, T. Thormählen, and H.-P. Seidel.

\medskip

[10] Pumarola, A., Sanchez, J., Choi, G., Sanfeliu, A., Moreno-Noguer, F.: 3DPeople:
Modeling the Geometry of Dressed Humans. In: International Conference in Computer Vision (ICCV) (2019)

\medskip

[11] Bertiche, H., Madadi, M., Escalera, S.: CLOTH3D: clothed 3d humans. vol.
abs/1912.02792 (2019)

\medskip

[12]Zheng, Z., Yu, T., Wei, Y., Dai, Q., Liu, Y.: Deephuman: 3d human reconstruction
from a single image. In: The IEEE International Conference on Computer Vision
(ICCV) (October 2019)

\medskip

[13] Yu, T., Zheng, Z., Guo, K., Zhao, J., Dai, Q., Li, H., Pons-Moll, G., Liu, Y.:
Doublefusion: Real-time capture of human performances with inner body shapes
from a single depth sensor. In: The IEEE International Conference on Computer
Vision and Pattern Recognition(CVPR). IEEE (June 2018)

\medskip

[14] Pons-Moll, G., Romero, J., Mahmood, N., Black, M.J.: Dyna: a model of dynamic
human shape in motion. ACM Transactions on Graphics 34, 120 (2015)

\medskip

[15] Bogo, F., Romero, J., Pons-Moll, G., Black, M.J.: Dynamic FAUST: Registering
human bodies in motion. In: IEEE Conf. on Computer Vision and Pattern Recognition (2017)

\medskip

[16] Zhu, H., Cao, Y., Jin, H., Chen, W., Du, D., Wang, Z., Cui, S., Han, X.: Deep
fashion3d: A dataset and benchmark for 3d garment reconstruction from single
images. arXiv preprint arXiv:2003.12753 (2020)